Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-27 manuscript/manuscript.Rmd
bit more discussion

>>>>

Conversely, our analysis suggests that, for high dimensional systems, bang-bang policies lead to increased sustainability and long-term profits as compared to constant mortality strategies.
Similarly, in App. \ref{app:tbd} we investigate several generalizations of the constant effort approach. 
For example, we examine strategies with a ramp-down from constant effort to zero effort at low populations.
These, too, yield subpar results as compared to escapement.
This seems to indicate that the ‘‘rest periods’’ so prominent in both the DRL solution and in the optimal bang-bang policy -- periods of several time steps with no fishing at all -- are important to maintain the sustainability of the fishery and, additionally, increase long-term profits.
